### 2011-11-26 AffineLieAlgebras/Thesis/1.tex
More translations in chapter 1.

\subsection{Branching for finite dimensional Lie algebras}
\label{sec:finite-dimens-lie}

\subsubsection{Regular embedding of $A_1$ into $B_2$}
\label{sec:regul-embedd-a_1}

Consider the regular embedding $A_1\to B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$
are presented as dashed vectors in Figure \ref{fig:B2_A1}. We denote the corresponding
Weyl reflections by $w_1, w_2$. The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is
grey.

\begin{figure}[p]
  \noindent\centering{
    \includegraphics[width=80mm]{figure1}
  }
  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$
  are presented as dashed vectors.
  The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is grey.
  The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is black.
  The weights of the singular element $\Psi^{(\omega_1)}$ are marked by circles with
  superscripts indicating the corresponding determinants $\epsilon(w)$.}
  \label{fig:B2_A1}

%\end{figure}
%\begin{figure}[pb]
  \noindent\centering{
    \includegraphics[width=80mm]{figure2}
  }
  \caption{Here in addition to the diagram presented above (Figure(\ref{fig:B2_A1}))
  the weights of $\left( \afb=A_1 \right)$-modules $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$
  originating in the points $\pi _{\af}\left[ u(\mu +\rho )-\rho \right] $
are shown by dotted lines.
    The superscripts over the highest weights  $\mu_{\af_{\perp }}\left( u\right)$
    are now the products $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.
    Coordinates along the root $\beta$ are counted in terms of the fundamental weight of $\af$. }
\label{fig:B2_A1_2}
\end{figure}

Let's perform the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$
($\omega_1$ -- the black vector in Figure \ref{fig:B2_A1}) according to the steps of the algorithm.
The root $\alpha_1$ is orthogonal to $\beta$,
so we have $\Delta_{\afb}^+ = \left\{ \alpha_1 \right\}$ (step (ii)).
According to Definition \ref{fan-definition}
the fan $\Gamma_{A_1\to B_2}$ (step (iii)) consists of two weights:
\begin{equation*}
  \label{eq:22}
  \Gamma_{A_1\to B_2}=\left\{ (1;2),\; (2;-1) \right\},
\end{equation*}
where the second component is the value of the sign function $s(\gamma)$.
Singular weights  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$ (step (iv))
are indicated by circles with the superscript $\epsilon\left( w \right)$.
The space $U$ is the factor $W/W_{\afb}$ where $W_{\afb}=\left\{e,w_1\right\}$.
This means that singular weights located above the $\beta$-line
belong to the Weyl chamber $\overline{C_{\widetilde{\af_{\perp }}}}$.
According to formula (\ref{defect-perp}) we have $\mathcal{D}_{\af_{\perp }}=0$ and
$\hf_{\perp }=0$, thus $\left\{ \mu _{\af_{\perp }}\left( w\right)
=\pi _{\af_{\perp }}\left[ w(\mu +\rho)-\rho \right]\right\}$.
We obtain four highest weights for $\af_{\perp }$-modules. In terms of
$\af_{\perp }$-fundamental weight $\frac{1}{2} \alpha_1$ these highest weights
$\left\{ \mu _{\af_{\perp }}\left( u\right)
=\pi _{\af_{\perp }}\left[ u(\mu +\rho)-\rho \right]| u \in U \right\}$
 are
$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$ (step v).
In Figure (\ref{fig:B2_A1_2}) the corresponding weight diagrams
$\left\{ \mathcal{N}_{\af_{\perp }}^{\mu _{\af_{\perp }}\left( u\right) }\right\} $
are attached to the set of $\af$-weights
$\left\{ \mu _{\af}\left( u\right)\right\} =\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]\right\}
=\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$.
In fact we do not need the
weight diagrams but only the dimensions of modules
$L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ multiplied by
$\epsilon \left( u\right) $ (step vi). Obtained values are to be attributed to the points
$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$
in $P_{\af}$. The singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
has the set of weights with anomalous multiplicities:
\begin{equation}
  \label{eq:25}
  \left\{(1;2),\; (0;-3),\; (-4;3),\; (-5;-2)\right\}.
\end{equation}

Applying formula (\ref{recurrent-relation}) with the fan
$\Gamma_{A_1\to B_2}$ to the set (\ref{eq:25}) (step vii)
we get zeros for the weights
greater than the highest anomalous vector $(1;2)$
and $k^{(1,0)}_1=2$ for the vector $(1;2)$ itself.
For the anomalous weight (0;-3) on the boundary of $\bar{C}^{(0)}_{\af}$ the recurrent relation gives
\begin{equation*}
  \label{eq:23}
  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1,
\end{equation*}
the branching is completed: $L_{B_2\downarrow A_1}^{\omega_1}=
2L_{A_1}^{\omega_{\left(A_1\right)} }
\bigoplus
L_{A_1}^{2\omega_{\left(A_1\right)} }$.

\subsubsection{Embedding $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the regular embedding $B_2 \rightarrow B_4$.
The corresponding Dynkin diagrams are presented in the Figure \ref{fig:dynkin}.
\begin{figure}[h]
  \centering
  \includegraphics[width=100mm]{figure3}
  \caption{The regular embedding $B_2 \rightarrow B_4$ described by dropping the node from the Dynkin diagram.
  Remember that here $\afb$ is equal to $B_2$ while the diagram
  shows only $A_1\oplus A_1$ (see Subsection \ref{sect-embeddings}).}
  \label{fig:dynkin}
\end{figure}

\begin{figure}[pt]
  \centering
    \includegraphics[width=100mm,height=90mm]{figure4}
  \caption{The singular element $e^{\gamma_0}\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
  displayed in the weight subspace $P_{\af}$ for $\af=B_2$ with the basis $\left\{e_3,e_4\right\}$.
  We see the projected singular weights $\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] +\gamma_0 | u \in U \right\}$
  shifted by $\gamma_0$ and supplied by multipliers
  $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.}
  \label{fig:B4B2anom}

%\end{figure}
%
%\begin{figure}[pb]
  \centering
  \includegraphics[height=80mm]{figure5}
  \caption{The fan $\Gamma$ for $B_2\rightarrow B_4$ with values of $s(\gamma+\gamma_0)$ attributed to each $\gamma \in \Gamma$.}
  \label{fig:B4B2Fan}
\end{figure}

In the orthonormal basis $\left\{e_1,\dots,e_4\right\}$ simple roots and positive roots of $B_4$ are
\begin{eqnarray*}
  \label{eq:19}
  S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\},\\[2mm]
 \Delta^+_{B_4}=\left\{ (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\right.\\
 \left. e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2\right\}
\end{eqnarray*}
The subalgebra $\af=B_2$ is fixed by the simple roots
\begin{equation*}
  \label{eq:26}
 S_{B_2}=\{e_3-e_4,e_4\}.
\end{equation*}
Its orthogonal counterpart $\afb=B_2$ has
\begin{eqnarray*}
  \label{eq:27}
  S_{\afb}=\{e_1-e_2,e_2\},\\
 \Delta^{+}_{\afb}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}.
\end{eqnarray*}
As far as the set $\Delta^+_{B_4} \setminus  \Delta^{+}_{\afb}$ is fixed the injection
fan $\Gamma_{B_2 \to B_4}$ can be constructed using Definition \ref{fan-definition}.
As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need only the factor
 $s\left(\gamma + \gamma_0\right)$.
The result is presented in Figure \ref{fig:B4B2Fan}.

Consider the $B_4$-module $L^{\mu}$ with the highest weight $\mu=2e_1 + 2 e_2 + e_3 + e_4$; \,
$\mathrm{dim}(L^{\left[0,1,0,2\right]})=2772$.
Here the defect is nontrivial, $\mathcal{D}_{\af_{\perp }}=-2\left( e_1 + e_2 \right)$,
while $\hf_{\bot}=0$. Among the singular weights there are
48 vectors with the property $\left\{ \mu _{\af_{\perp }%
}\left( u\right) =\pi _{\af_{\perp }}\left[ u(\mu +\rho
)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\af_{\perp }}}\right\} $.
The set $U=\left\{ u \right\}$ is thus fixed.
Compute the dimensions of the corresponding $\afb$-modules with the highest weights
$ \mu _{\af_{\perp }}\left( u\right)$ (using the Weyl dimension formula) and multiply them
by $\epsilon\left( u \right)$. The result is the singular element
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ shown in Figure \ref{fig:B4B2anom}.

Now one can place the fan $\Gamma$ (see Figure \ref{fig:B4B2Fan}) in the highest of the weights
presented in Figure \ref{fig:B4B2anom} and start the recursive determination of the branching coefficients
(using relation (\ref{recurrent-relation})):
\begin{eqnarray*}
  \label{eq:24}
  \pi_{\af} \left(ch L^{\left[0,1,0,2\right]}_{B_4}\right) = 6 \; ch L^{\left[0,0\right]}_{B_2}+ 60
  \; ch L_{B_2}^{\left[0,2\right]}+ 30 \; ch L_{B_2}^{\left[1,0\right]}+ 19 \; ch L_{B_2}^{\left[2,0\right]}+\\
  40 \; ch L_{B_2}^{\left[1,2\right]}+ 10 \; ch L_{B_2}^{\left[0,4\right]}.
\end{eqnarray*}
%\newpage
\subsection{Applications to conformal field theory}
\label{sec:phys-appl}

\subsubsection{Conformal embeddings}
\label{sec:conformal-embeddings}

Branching coefficients for an embedding of affine Lie algebra into
affine Lie algebra can be used to construct modular invariant
partition functions for Wess-Zumino-Novikov-Witten models in conformal field theory
(\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
In these models current algebras are affine Lie algebras.

The modular invariant partition function is crucial for the conformal theory to be valid
on the torus and higher genus Riemann surfaces. It is important for the applications of
CFT to string theory and to critical phenomena description.

The simplest modular-invariant partition function has the diagonal form:
\begin{equation}
  \label{eq:34}
   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
\end{equation}
Here the sum is over the set of highest weights for integrable modules in a WZW-model
and $\chi_{\mu}(\tau)$ are the normalized characters (see \cite{difrancesco1997cft}) of these modules.

To construct nondiagonal modular invariants is not an easy problem,
although for some models the complete classification of modular invariants is known \cite{1994hepthGannon,1995JMPGannon}.

Consider the Wess-Zumino-Witten model with the affine Lie algebra $\af$.
Nondiagonal modular invariants for this model can be constructed from the diagonal
invariant if there exists an affine algebra $\mathfrak{g}$ such that $\af\subset\mathfrak{g}$.
Then we can replace the characters of the $\mathfrak{g}$-modules in the diagonal
modular invariant partition function (\ref{eq:34})
by the decompositions
\begin{equation*}
  \label{eq:32}
\sum_{\nu \in P^{+}_{\af}}b^{(\mu)}_{\nu} \chi_{\nu}
\end{equation*}
containing normalized characters $\chi_{\nu}$ of the corresponding $\af$-modules.
Thus we obtain a nondiagonal modular-invariant  partition function for the theory with
the current algebra $\af$,
\begin{equation}
  \label{eq:36}
   Z_{\af}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\af}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau).
\end{equation}

The effective reduction procedure is crucial for this construction.
The embedding is required to preserve the conformal invariance.
Let $X^{\alpha_j}_{-n_j}$ and $\tilde{X}^{\alpha'_j}_{-n_j}$ be the lowering generators for
$\mathfrak{g}$ and for $\af\subset\mathfrak{g}$ correspondingly.
Let $\pi_{\af}$ be the projection operator of
$\pi_{\af}:\mathfrak{g}\longrightarrow \af$.
In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$
the states can be described as
\begin{equation*}
  \label{eq:109}
  X^{\alpha_1}_{-n_1}X^{\alpha_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
\end{equation*}
And for the sub-algebra $\af$ the corresponding states are
\begin{equation*}
  \label{eq:110}
  \tilde{X}^{\alpha'_1}_{-n_1}\tilde{X}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\af}(\lambda)\right>.
\end{equation*}
The $\mathfrak{g}$-invariance of the vacuum entails its $\af$-invariance,
but this is not the case for the energy-momentum tensor. So the energy-momentum tensor of the larger theory
should contain only the generators $\tilde{X}$. Then the relation
\begin{equation}
  \label{eq:2}
  T_{\mathfrak{g}}(z)=T_{\af}(z)
\end{equation}
leads to the equality of central charges
\begin{equation*}
  \label{eq:33}
  c(\mathfrak{g})=c(\af)
\end{equation*}
and to the relation
\begin{equation}
  \label{eq:111}
  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\af}{x_ek+a}.
\end{equation}
Here $x_e$ is the so called "embedding index":
$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$
with $\Theta$, $\Theta_{\mathfrak{a}}$ being the highest roots of
$\mathfrak{g}$ and $\mathfrak{a}$
while $g$  and $a$ are the  corresponding dual Coxeter numbers.

It can be demonstrated that solutions of equation (\ref{eq:111}) exist only
for the level $k=1$ \cite{difrancesco1997cft}.

The complete classification of conformal embeddings is given in \cite{schellekens1986conformal}.

The relation (\ref{eq:111}) and the asymptotics of the branching functions can be used
to prove the finite reducibility theorem \cite{kac1988modular}.
It states that for a conformal embedding  $\af\longrightarrow\mathfrak{g}$
only finite number of branching coefficients have nonzero values.

>>>>

\subsection{Ветвления модулей конечномерных алгебр Ли}
\label{sec:finite-dimens-lie}

\subsubsection{Регулярное вложение $A_1$ в $B_2$}
\label{sec:regul-embedd-a_1}

Рассмотрим регулярное вложение $A_1\to B_2$. Простые корни $\alpha_1, \alpha_2$ алгебры $B_2$ обозначены пунктирными стрелками на Рисунке \ref{fig:B2_A1}. Мы обозначаем соответствующие элементарные отражения через $w_1, w_2$. Простой корень $\beta = \alpha_1+2\alpha_2$ алгебры $A_1$ показан серым цветом.

\begin{figure}[p]
  \noindent\centering{
    \includegraphics[width=80mm]{figure1}
  }
  \caption{Регулярное вложение  $A_1$ в $B_2$. Простые корни  $\alpha_1, \alpha_2$ алгебры $B_2$ обозначены пунктирными стрелками. Простой корень $\beta = \alpha_1+2\alpha_2$ подалгебры $A_1$ показан серым цветом. Старший вес фундаментального представления $L^{(1,0)=\omega_1}_{B_2}$ выделен черным. Веса сингулярного элемента $\Psi^{(\omega_1)}$ отмечены кругами с подписанными значениями соответствующих определителей $\epsilon(w)$.}
  \label{fig:B2_A1}

%\end{figure}
%\begin{figure}[pb]
  \noindent\centering{
    \includegraphics[width=80mm]{figure2}
  }
  \caption{Здесь диаграмма, показанная выше (Рисунок \ref{fig:B2_A1}), дополнена весами $\left( \afb=A_1 \right)$-модулей $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$, построенных в точках $\pi _{\af}\left[ u(\mu +\rho )-\rho \right] $ и показанных пунктирными линиями. 
    Подписи к старшим весам   $\mu_{\af_{\perp }}\left( u\right)$ представляют собой значения произведений $\epsilon(u)\dim\left(L_{\afb}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.
    Координаты вдоль корня $\beta$ указаны по отношению к фундаментальному весу $\af$. }
\label{fig:B2_A1_2}
\end{figure}

Выполним редукцию фундаментального представления  $L^{(1,0)=\omega_1}_{B_2}$ ($\omega_1$ -- черная стрелка на Рисунке \ref{fig:B2_A1}) в соответствии с алгоритмом.
Корень $\alpha_1$ ортогонален к $\beta$, так что  $\Delta_{\afb}^+ = \left\{ \alpha_1 \right\}$ (шаг (ii)).
В соответствии с Определением \ref{fan-definition} веер вложения $\Gamma_{A_1\to B_2}$ (шаг (iii)) состоит из двух весов:
\begin{equation*}
  \label{eq:22}
  \Gamma_{A_1\to B_2}=\left\{ (1;2),\; (2;-1) \right\},
\end{equation*}
где вторая компонента -- это значение знаковой функции  $s(\gamma)$.
Сингулярные веса  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$ (шаг (iv)) показаны кругами с подписанными значениями $\epsilon\left( w \right)$. Пространство  $U$ представляет собой факторпространство $W/W_{\afb}$, где $W_{\afb}=\left\{e,w_1\right\}$. Это означает, что сингулярные веса, находящиеся над прямой, заданной корнем $\beta$, принадлежат главной камере Вейля $\overline{C_{\widetilde{\af_{\perp }}}}$. Из формулы (\ref{defect-perp})  мы получаем  $\mathcal{D}_{\af_{\perp }}=0$ и $\hf_{\perp }=0$, то есть $\left\{ \mu _{\afb}\left( w\right)=\pi _{\afb}\left[ w(\mu +\rho)-\rho \right]\right\}$. Значит есть четыре старших веса для $\af_{\perp }$-модулей.  В базисе фундаментального веса $\frac{1}{2} \alpha_1$ алгебры $\afb$ координаты этих весов
$\left\{ \mu _{\afb}\left( u\right)=\pi _{\afb}\left[ u(\mu +\rho)-\rho \right]| u \in U \right\}$
равны
$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$ (шаг v).
На Рисунке (\ref{fig:B2_A1_2}) соответствующие весовые диаграммы
$\left\{ \mathcal{N}_{\af_{\perp }}^{\mu _{\af_{\perp }}\left( u\right) }\right\} $
построены из весов $\left\{ \mu _{\af}\left( u\right)\right\} =\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]\right\}
=\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$ подалгебры   $\af$.
В действительности весовые диаграммы нам не нужны, достаточно знать лишь размерности модулей
$L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ умноженные на
$\epsilon \left( u\right) $ (шаг vi). Полученные значения должны быть связаны с точками
$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$ в $P_{\af}$. Сингулярный элемент $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ содержит следующий набор весов и их сингулярных кратностей:
\begin{equation}
  \label{eq:25}
  \left\{(1;2),\; (0;-3),\; (-4;3),\; (-5;-2)\right\}.
\end{equation}

Применяя формулу (\ref{recurrent-relation}) с веером
$\Gamma_{A_1\to B_2}$ к множеству (\ref{eq:25}) (шаг vii)
мы получаем нули для весов больше старшего сингулярного вектора$(1;2)$ и  $k^{(1,0)}_1=2$ для самого вектора $(1;2)$.
Для сингулярного веса $(0;-3)$ на границе $\bar{C}^{(0)}_{\af}$ рекуррентное соотношение дает
\begin{equation*}
  \label{eq:23}
  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1,
\end{equation*}
и редукция завершена: $L_{B_2\downarrow A_1}^{\omega_1}=
2L_{A_1}^{\omega_{\left(A_1\right)} }
\bigoplus
L_{A_1}^{2\omega_{\left(A_1\right)} }$.

\subsubsection{Вложение  $B_2$ в $B_4$}
\label{sec:someth-high-dimens}
Рассмотрим регулярное вложение $B_2 \rightarrow B_4$. Соответствующие диаграммы Дынкина показаны на Рисунке \ref{fig:dynkin}.
\begin{figure}[h]
  \centering
  \includegraphics[width=100mm]{figure3}
  \caption{Регулярное вложение  $B_2 \rightarrow B_4$ получается путем исключения вершины из диаграммы Дынкина. 
    Напомним, что в данном случае $\afb$ равна $B_2$, тогда как на диаграмме видна только подалгебра $A_1\oplus A_1$ (см. раздел \ref{sect-embeddings}).}
  \label{fig:dynkin}
\end{figure}

\begin{figure}[pt]
  \centering
    \includegraphics[width=100mm,height=90mm]{figure4}
  \caption{Сингулярный элемент  $e^{\gamma_0}\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ показан в весовом подпространстве $P_{\af}$, где $\af=B_2$ и базис равен $\left\{e_3,e_4\right\}$. Показаны спроектированные сингулярные веса $\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] +\gamma_0 | u \in U \right\}$, сдвинутые на  $\gamma_0$ и снабженные множителям  $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.}
  \label{fig:B4B2anom}

%\end{figure}
%
%\begin{figure}[pb]
  \centering
  \includegraphics[height=80mm]{figure5}
  \caption{Веер $\Gamma$ для вложения $B_2\rightarrow B_4$ со значениями функции $s(\gamma+\gamma_0)$, указанными при соответствующих весах $\gamma \in \Gamma$.}
  \label{fig:B4B2Fan}
\end{figure}

В ортогональном базисе $\left\{e_1,\dots,e_4\right\}$ простые и положительные алгебры $B_4$ равны
\begin{eqnarray*}
  \label{eq:19}
  S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\},\\[2mm]
 \Delta^+_{B_4}=\left\{ (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\right.\\
 \left. e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2\right\}
\end{eqnarray*}
Подалгебра  $\af=B_2$ задается простыми корнями
\begin{equation*}
  \label{eq:26}
 S_{B_2}=\{e_3-e_4,e_4\}.
\end{equation*}
Ее ортогональный партнер $\afb=B_2$ определяется корнями
\begin{eqnarray*}
  \label{eq:27}
  S_{\afb}=\{e_1-e_2,e_2\},\\
 \Delta^{+}_{\afb}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}.
\end{eqnarray*}
После определения множества $\Delta^+_{B_4} \setminus  \Delta^{+}_{\afb}$ можно построить веер вложения $\Gamma_{B_2 \to B_4}$ применяя Определение \ref{fan-definition}. Так как для этого вложения $s\left( \gamma_0\right)=-1$, в рекуррентном соотношении нам нужен только множитель $s\left(\gamma + \gamma_0\right)$. Результат построения веера показан на Рисунке \ref{fig:B4B2Fan}.

Рассмотрим модуль $L^{\mu}$ алгебры  $B_4$ со старшим весом $\mu=2e_1 + 2 e_2 + e_3 + e_4$; \,
$\mathrm{dim}(L^{\left[0,1,0,2\right]})=2772$.
В данном случае дефект не тривиален, $\mathcal{D}_{\af_{\perp }}=-2\left( e_1 + e_2 \right)$, тогда как $\hf_{\bot}=0$. Среди сингулярных весов есть 
48 векторов со свойством $\left\{ \mu _{\afb}\left( u\right) =\pi _{\af_{\perp }}\left[ u(\mu +\rho)-\rho \right] -\mathcal{D}_{\afb}\in \overline{C_{\afb}}\right\} $.
Таким образом мы определили множество $U=\left\{ u \right\}$. Вычислим размерности соответствующих  $\afb$-модулей со старшими весами $\mu_{\afb}\left( u\right)$ (используем формулу Вейля для размерностей) и умножим их на $\epsilon\left( u \right)$. В результате получим сингулярный элемент
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$, показанный на Рисунке \ref{fig:B4B2anom}.

Теперь поместим веер  $\Gamma$ (см. Рисунок \ref{fig:B4B2Fan}) в старший из весов, показанных на Рисунке \ref{fig:B4B2anom} и проведем рекурсивное вычисление коэффициентов ветвления (с использованием соотношения (\ref{recurrent-relation})):
\begin{eqnarray*}
  \label{eq:24}
  \pi_{\af} \left(ch L^{\left[0,1,0,2\right]}_{B_4}\right) = 6 \; ch L^{\left[0,0\right]}_{B_2}+ 60
  \; ch L_{B_2}^{\left[0,2\right]}+ 30 \; ch L_{B_2}^{\left[1,0\right]}+ 19 \; ch L_{B_2}^{\left[2,0\right]}+\\
  40 \; ch L_{B_2}^{\left[1,2\right]}+ 10 \; ch L_{B_2}^{\left[0,4\right]}.
\end{eqnarray*}
%\newpage
\subsection{Примеры приложений в конформной теории поля}
\label{sec:phys-appl}

\subsubsection{Конформные вложения}
\label{sec:conformal-embeddings}

Как мы уже объясняли в разделе \ref{sec:modular-invariance}, коэффициенты ветвления для вложения аффинной алгебры Ли в аффинную алгебру Ли можно использовать для построения модулярно-инвариантной статсуммы для моделей Весса-Зумино-Новикова-Виттена в двумерной конформной теории поля (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
В этих моделях аффинные алгебры Ли являются алгебрами токов.

Модулярная инвариантность статсуммы необходима для самосогласованности теории на торе и римановых поверхностях высшего рода, что важно для приложений конформной теории поля в теории струн и описании критического поведения.

Простейшая модулярно-инвариантная статсумма имеет диагональный вид:
\begin{equation}
  \label{eq:34}
   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
\end{equation}
Здесь суммирование ведется по множеству старших весов интегрируемых модулей в ВЗНВ-модели, а $\chi_{\mu}(\tau)$ -- это нормированные характеры (см. \cite{difrancesco1997cft}) этих модулей.

Построение недиагональных модулярных инвариантов -- это нетривиальная проблема, хотя для некоторых моделей известна полная классификация модулярных инвариантов \cite{1994hepthGannon,1995JMPGannon}.

Рассмотрим модель Весса-Зумино-Новикова-Виттена с аффинной алгеброй Ли $\af$. Недиагональные модулярные инварианты этой модели могут быть построены из диагонального инварианта, если существует аффинная алгебра  $\mathfrak{g}$, такая, что $\af\subset\mathfrak{g}$. Тогда мы можем заменить характеры  $\mathfrak{g}$-модулей в диагональной модулярно-инвариантной статсумме (\ref{eq:34}) на разложения
\begin{equation*}
  \label{eq:32}
\sum_{\nu \in P^{+}_{\af}}b^{(\mu)}_{\nu} \chi_{\nu},
\end{equation*}
содержащие нормированные характеры $\chi_{\nu}$ соответствующих $\af$-модулей. В результате мы получим недиагональную модулярно-инвариантную статсумму для теории с алгеброй токов $\af$,
\begin{equation}
  \label{eq:36}
   Z_{\af}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\af}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau).
\end{equation}

Эффективная процедура редукции существенна для этой конструкции. Вложение должно сохранять конформную инвариантность. Пусть $X^{\alpha_j}_{-n_j}$ и $\tilde{X}^{\alpha'_j}_{-n_j}$ -- понижающие операторы для алгебры $\mathfrak{g}$ и подалгебры $\af\subset\mathfrak{g}$ соответственно. Обозначим через $\pi_{\af}$ оператор проекции $\pi_{\af}:\mathfrak{g}\longrightarrow \af$. В теории, связанной с $\mathfrak{g}$ и вакуумом $\left|\lambda\right>$ состояния строятся как
\begin{equation*}
  \label{eq:109}
  X^{\alpha_1}_{-n_1}X^{\alpha_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
\end{equation*}
А для подалгебры $\af$ соответствующие состояния имеют вид
\begin{equation*}
  \label{eq:110}
  \tilde{X}^{\alpha'_1}_{-n_1}\tilde{X}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\af}(\lambda)\right>.
\end{equation*}
Инвариантность вакуума под действием $\mathfrak{g}$ влечет его инвариантность относительно действия $\af$, но это неверно для тензора энергии-импульса. Необходимо, чтобы тензор энергии-импульса объемлющей теории содержал только генераторы $\tilde{X}$. Тогда соотношение
\begin{equation}
  \label{eq:2}
  T_{\mathfrak{g}}(z)=T_{\af}(z)
\end{equation}
ведет к равенству центральных зарядов
\begin{equation*}
  \label{eq:33}
  c(\mathfrak{g})=c(\af)
\end{equation*}
и к уравнению
\begin{equation}
  \label{eq:111}
  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\af}{x_ek+a}.
\end{equation}
Здесь $x_e$ -- так называемый ``индекс вложения'':
$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$, где $\Theta$, $\Theta_{\mathfrak{a}}$ -- старшие корни алгебр
$\mathfrak{g}$ и $\mathfrak{a}$, а  $g$ и $a$ -- соответствующие дуальные числа Кокстера.

Можно показать, что решения уравнения (\ref{eq:111}) существуют только для уровня $k=1$ \cite{difrancesco1997cft}.

Полная классификация конформных вложения дана в работе \cite{schellekens1986conformal}.

Соотношение (\ref{eq:111}) и асимптотика функций  and the asymptotics of the branching functions can be used
to prove the finite reducibility theorem \cite{kac1988modular}.
It states that for a conformal embedding  $\af\longrightarrow\mathfrak{g}$
only finite number of branching coefficients have nonzero values.
